Fail Faster

### 2025-03-25 paper/paper.tex
last bcp nits

Changing the shape of the test input distribution is perhaps the most well-studied way to accelerate bug-finding in PBT.
 Feedback-driven mechanisms
like Targeted PBT~\cite{loscherTargetedPropertybasedTesting2017} and
Coverage-Guided PBT~\cite{lampropoulosCoverageGuidedProperty2019}
speed up testing by changing the generation order to find
``interesting'' inputs faster. Separately, enumerative approaches to
PBT~\cite{runcimanSmallcheckLazySmallcheck2008,braquehaisSimpleIncrementalDevelopment2017}
try to get to bugs faster by leveraging the ``small-scope
hypothesis,'' which posits that most bugs will be triggered by smallish
inputs. All of these approaches can have significant performance
benefits in
practice, but they are largely orthogonal to our contributions; we expect
\name{} could be used to speed these existing techniques to varying
degrees. \bcp{Namely: the staging part would be equally effective, but
the RNG part would be either less or not relevant.}

>>>>

Changing the shape of the test input distribution is perhaps the most well-studied way to accelerate bug-finding in PBT.
 Feedback-driven mechanisms
like Targeted PBT~\cite{loscherTargetedPropertybasedTesting2017} and
Coverage-Guided PBT~\cite{lampropoulosCoverageGuidedProperty2019}
speed up testing by changing the generation order to find
``interesting'' inputs faster. Separately, enumerative approaches to
PBT~\cite{runcimanSmallcheckLazySmallcheck2008,braquehaisSimpleIncrementalDevelopment2017}
try to get to bugs faster by leveraging the ``small-scope
hypothesis,'' which posits that most bugs will be triggered by smallish
inputs. All of these approaches can have significant performance
benefits in
practice, but they are largely orthogonal to our contributions; we expect
both \name{} and faster \rands{} could be used to speed these existing techniques to varying
degrees.
